\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-08 doc/paper.tex
discussing problems during the iteration

>>>>

During the fixed-point iteration several problems can appear.  First
of all, the iteration is not guaranteed to converge.  If the desired
accuracy goal is not achieved with the given maximum number of
iterations, \fs will set the \code{no_convergence} flag in the
\code{Problems} class.  This class monitors the problem status of the
spectrum generator during the iteration and can be obtained from the
model class via the \code{get_problems()} function.  Besides
non-convergence, solving the EWSB conditions
\eqref{eq:one-loop-ewsb-eq} numerically with the desired accuracy
might fail.  In this case the \code{no_ewsb} flag is set.
Furthermore, in intermediate iteration steps tachyonic states might
appear, which are ignored but nevertheless monitored in the
\code{Problems} class.  If tachyons still exist after the iteration
has converged the mass spectrum is marked as invalid by setting entry
$4$ in the \code{SPINFO} block in the SLHA output file.  Finally,
during the RG running some couplings might become non-perturbative.
In this case the iteration stops setting the \code{no_perturbative}
flag.
